---
title: "API Test Suite"
author: "Alex Gold"
date: "10/18/2019"
output: html_document
---

```{r}
library(httr)
library(dplyr)

plumb_url <- "http://127.0.0.1:7825"
url <- function(x) glue::glue("{plumb_url}/{x}")
num <- round(runif(1) * 10000000)
uni <- function(x) {paste0(x, num)}

to_df <- function(x) x %>% httr::content() %>% bind_rows()
```

# Test Classrooms
### Create Classroom
Test normal
```{r}
res <- httr::POST(url("class"), 
                   body = list(name = uni("my_class"), 
                               password = uni("test_pass"), 
                               description = "A test classroom."), 
                   encode = "json") %>%
   to_df()

stopifnot(res$name == uni("my_class"))
stopifnot(res$password == uni("test_pass"))
```

Dupe name/password
```{r}
# Should err b/c names and passwords need to be unique
res <- httr::POST(url("class"), 
                   body = list(name = uni("my_class"), 
                               password = uni("test_pass"), 
                               description = "A test classroom."), 
                   encode = "json")

stopifnot(res$status_code == 400)
stopifnot(stringr::str_detect(content(res), "unique"))
```

No Description
```{r}
# Should work without providing description
res <- httr::POST(url("class"), 
                   body = list(name = uni("my_class2"), 
                               password = uni("test_pass2")), 
                   encode = "json") %>%
  to_df()

stopifnot(res$description == "")
```
 
### Get Classroom
```{r}
res <- httr::GET(url("class")) %>%
  to_df()

stopifnot(uni("my_class") %in% res$name)
stopifnot(uni("my_class2") %in% res$name)
```

## Attributes
### GET
```{r}
id <- filter(res, name == uni("my_class")) %>% pull(classroomid)

attr1 <- httr::GET(url("class_attr"), 
                   query = list(class_id = id, 
                               attr = "name"), 
                   encode = 'json') %>%
  content()
```

```{r}
stopifnot(attr1[[1]]$name == uni("my_class"))
```


### Change
```{r}
attr_ch <- httr::POST(url("class_attr"), 
                      query = list(class_id = id, 
                                  attr = "name", 
                                  value = uni("my_class_update"))) %>%
  to_df()
```

```{r}
stopifnot(attr_ch$name == uni("my_class_update"))
```


### Archive
```{r}
arch <- httr::POST(url("class_attr"), 
                      query = list(class_id = id, 
                                  attr = "status", 
                                  value = "ARCHIVE")) %>%
  to_df()

stopifnot(arch$name %>% stringr::str_detect("^ARCHIVE"))
stopifnot(arch$description %>% stringr::str_detect("^ARCHIVE"))
stopifnot(arch$password %>% stringr::str_detect("^ARCHIVE"))
stopifnot(arch$status %>% stringr::str_detect("^ARCHIVE"))

# Error
reactiv <- httr::POST(url("class_attr"), 
                      query = list(class_id = id, 
                                  attr = "status", 
                                  value = "ACTIVE")) %>% 
  content()

stopifnot(stringr::str_detect(reactiv, "Cannot reactivate"))
```

# Students
New classroom
```{r}
class_id <- httr::POST(url("class"), 
                   body = list(name = uni("student_test_class"), 
                               password = uni("student_test_pass"), 
                               description = "Tester for student creation"), 
                   encode = "json") %>%
   to_df() %>% 
  pull(classroomid)
```

## Create
```{r}
res <- httr::POST(url("student"), 
                   body = list(name = "Anakin Skywalker", 
                               email = "lightside@jedi.org", 
                               class_id = class_id), 
                   encode = "json") %>%
   to_df()
```

```{r}
stopifnot(res$name == "Anakin Skywalker")
stopifnot(res$email == "lightside@jedi.org")
```

## Get
```{r}
res <- httr::GET(url("student")) %>% 
  to_df()

stopifnot(is.data.frame(res))
```

```{r}
res <- httr::GET(url('student'), 
                 query = list(class_id = class_id)) %>%
  to_df()
student_id <- res$studentid

stopifnot(res$name == "Anakin Skywalker")
```

## Get Attribute
```{r}
res <- httr::GET(url("student_attr"), 
                 query = list(attr = "name", 
                              class_id = class_id, 
                              student_id = student_id)) %>% 
  to_df()
stopifnot(res$name == "Anakin Skywalker")
```

## Set Attribute
```{r}
res <- httr::POST(url("student_attr"), 
                  body = list(attr = "name", 
                              class_id = class_id, 
                              student_id = student_id, 
                              value = "Darth Vader"), 
                  encode = 'json') %>%
  to_df() 
stopifnot(res$name == "Darth Vader")
```

# Instances
## Create
```{r}
res <- httr::POST(url("instance"), 
                  body = list(class_id = class_id, 
                              identifier = uni("inst"), 
                              url = paste(uni("http://"), ".com"), 
                              username = "inst_user", 
                              password = "inst_pass"), 
                  encode = 'json') %>%
  to_df()
stopifnot(res$url == paste(uni("http://"), ".com"))
```

## URL Checking
Should err
```{r}
res <- httr::POST(url("instance"), 
                  body = list(class_id = class_id, 
                              identifier = "inst1", 
                              url = "h://instance.com", 
                              username = "inst_user", 
                              password = "inst_pass"), 
                  encode = 'json') %>%
  content()

stopifnot("error" %in% names(res))
```

## Get
```{r}
res <- httr::GET(url("instance"), 
                 query = list(class_id = class_id)) %>%
  to_df()
stopifnot(res$url == paste(uni("http://"), ".com"))
instance_id <- res$instanceid
```

## Get Attribute
```{r}
res <- httr::GET(url("instance_attr"), 
                 query = list(class_id = class_id, 
                              instance_id = instance_id, 
                              attr = "url")) %>%
  to_df()
stopifnot(res$url == paste(uni("http://"), ".com"))
```

## Set Attribute
```{r}
res <- httr::POST(url("instance_attr"), 
                 body = list(class_id = class_id, 
                              instance_id = instance_id, 
                              attr = "url", 
                             value = paste(uni("http://redo"), ".com")), 
                 encode = "json") %>%
  to_df()
stopifnot(res$url == paste(uni("http://redo"), ".com"))
```

### Invalid URL
Should err
```{r}
res <- httr::POST(url("instance_attr"), 
                 body = list(class_id = class_id, 
                              instance_id = instance_id, 
                              attr = "url", 
                             value = "httadsfp://notaninstance.com"), 
                 encode = "json") %>% 
  content()
stopifnot(res$error == "URL malformed.")
```

## Claim Instance

```{r}
# No instance id
res <- httr::POST(url("claim_instance"), 
                  body = list(class_id = class_id, 
                              student_id = student_id), 
                  encode = "json") %>% 
  to_df()
stopifnot(res$classroomid == class_id)
stopifnot(res$studentid == student_id)
stopifnot(is.numeric(res$instanceid))

# With instance id
instance_id <- httr::POST(url("instance"), 
                  body = list(class_id = class_id, 
                              identifier = uni("inst_new"), 
                              url = paste(uni("http://inst_new"), ".com"), 
                              username = "inst_user", 
                              password = "inst_pass"), 
                  encode = 'json') %>%
  to_df() %>%
  pull(instanceid)

student_id <- httr::POST(url("student"), 
                   body = list(name = "Luke Skywalker", 
                               email = "reallylightside@jedi.org", 
                               class_id = class_id), 
                   encode = "json") %>%
   to_df() %>%
  pull(studentid)
res <- httr::POST(url("claim_instance"), 
                  body = list(class_id = class_id, 
                              student_id = student_id, 
                              instance_id = instance_id), 
                  encode = "json") %>% 
  to_df()
stopifnot(res$classroomid == class_id)
stopifnot(res$instanceid == instance_id)
stopifnot(res$studentid == student_id)
```

## Check Student-Instance mapping
```{r}
res <- httr::GET(url("student_instances"), 
                 query = list(class_id = class_id), 
                 encode = "json") %>%
  to_df()
test <- res %>% filter(instance_identifier == uni("inst_new"))
stopifnot(test$class_name == uni("student_test_class"))
stopifnot(test$student_name == "Luke Skywalker")
```

# Events
## Add
```{r}
res <- httr::POST(url("event"), 
                  body = list(event = "Big fight", 
                              session = 123), 
                  encode = "json") %>%
  to_df()
event_id <- res$eventid
```

## GET
```{r}
res <- httr::GET(url("event")) %>%
  to_df()
stopifnot("Big fight" %in% res$event)
```

## Event Attr
```{r}
res <- httr::GET(url("event_attr"), 
                 query = list(attr = "event", 
                              event_id = event_id)) %>%
  to_df()
stopifnot(res$event == "Big fight")
```


